### 2014-10-30 transactions.tex
Edits throughout

In order to illustrate the utility of declarative reasoning for transactions,
let us extend our running bank account example with use two accounts (objects)
-- current ($c$) and savings ($s$). Each account provides operations
\cf{withdraw}, \cf{deposit} and \cf{getBalance}, with the same contracts as
defined previously. We consider two transactions -- \cf{save(amt)}, which
transfers \cf{amt} from current to savings, and \cf{totalBalance} returns
the sum of the balances of individual accounts. The pseudo code for the
transactions is given below:
\vspace{-1em}

\noindent \begin{minipage}[t]{0.5\columnwidth}
\begin{codepython}
def save(amt):
  atomically psi1 :
    b = c.withdraw(amt)
    if (b): s.deposit(amt)
\end{codepython}
\end{minipage}
\begin{minipage}[t]{0.5\columnwidth}
\begin{codepython}
def totalBalance():
  atomically psi2 :
    b1 = c.getBalance()
    b2 = s.getBalance()
    return b1 + b2
\end{codepython}
\end{minipage}

\noindent where $\cv_1$ and $\cv_2$ are the contracts on the corresponding
transactions. Our goal is to ensure that \cf{totalBalance} returns the result
obtained from a consistent snapshot of the object states.

>>>>

In order to illustrate the utility of declarative reasoning for transactions,
let us extend our running bank account example with use two accounts (objects)
-- current ($c$) and savings ($s$). Each account provides operations
\cf{withdraw}, \cf{deposit} and \cf{getBalance}, with the same contracts as
defined previously. We consider two transactions -- \cf{save(amt)}, which
transfers \cf{amt} from current to savings, and \cf{totalBalance} returns the
sum of the balances of individual accounts. The \name code for the transactions
is given below:
\vspace{-1em}

\noindent \begin{minipage}[t]{0.5\columnwidth}
\begin{codehaskell}
save :: Quelea ()
save amt =
  x <- $(chkTxn psi1)
  atomically x $ do
    b <- withdraw c amt
    when b $ deposit s amt
\end{codehaskell}
\end{minipage}
\begin{minipage}[t]{0.5\columnwidth}
\begin{codehaskell}
totalBalance :: Quelea Int
totalBalance =
  x <- $(chkTxn psi2)
  atomically x $ do
    b1 <- getBalance s
    b2 <- getBalance s
    return b1 + b2
\end{codehaskell}
\end{minipage}

\noindent In the above code example, the operations on bank account are simply
wrappers around the store interface. For example,

\begin{codehaskell}
withdraw :: Key -> Int -> Quelea Bool
withdraw k amt = invoke k Withdraw amt
\end{codehaskell}

\noindent $\cv_1$ and $\cv_2$ are the contracts on the corresponding
transactions. Our goal is to ensure that \cf{totalBalance} returns the result
obtained from a consistent snapshot of the object states.
